The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-30 ms.Rmd
Wrap long error messages. But might mess up syntax highlighting.
More code tidying.

```{r fengChangeWorkflow, eval = TRUE, fig.show = 'hide'}
Feng_Papes_interactive <- ChangeWorkflow(
    Feng_Papes,
    output = Chain(PerformanceMeasures, 
                   PrintMap, 
                   InteractiveMap, 
                   ResponseCurve))
```

>>>>

```{r fengChangeWorkflow, eval = TRUE, fig.show = 'hide'}
Feng_Papes_interactive <- 
  ChangeWorkflow(workflow = Feng_Papes,
                   output = Chain(PerformanceMeasures, 
                                  PrintMap, 
                                  InteractiveMap, 
                                  ResponseCurve))
```
